---
title: "E-commerce Cosmetics"
author: "Nathan"
date: "12/17/2019"
output: html_document
---

# Exploratory data analysis of an e-commerce cosmetics shop from October 2019 to November 2019.
# source: https://www.kaggle.com/mkechinov/ecommerce-events-history-in-cosmetics-shop


# Let's load our packages and disable scientific notation.
```{r results = 'hide', message=FALSE, warning=FALSE}
library(tidyverse)
options(scipen = 999)
```


# Load in the two csv files and combine them into one data.frame.
```{r}
oct2019 <- read.csv("C:/workspaceR/eCommerce_cosmetics/oct2019.csv", stringsAsFactors=FALSE)
nov2019 <- read.csv("C:/workspaceR/eCommerce_cosmetics/nov2019.csv", stringsAsFactors=FALSE)
df <- bind_rows(oct2019, nov2019)

```


# Examine data.
```{r}
df %>% head()
df %>% str()
```


# What are the most purchased brands?
```{r}
df %>% 
  filter(event_type == 'purchase') %>% 
  group_by(brand) %>% 
  count(sort = TRUE) %>% 
  filter(!brand == "")
```


# Who purchased the most products and what do they buy?
```{r}
top_buyer<- df %>% 
              filter(event_type == 'purchase') %>% 
              group_by(user_id) %>% 
              count(sort = TRUE) %>% 
              head(1) %>% 
              pull(user_id)
top_buyer

df %>% 
  filter(event_type == 'purchase' & user_id == top_buyer) %>% 
  group_by(product_id) %>% 
  count(sort = TRUE)
```


# Who are the top 5 buyers in terms of dollar amount? 
```{r}
df %>% 
  filter(event_type == 'purchase') %>% 
  group_by(user_id) %>% 
  summarize(dollars_spent = sum(price)) %>% 
  arrange(-dollars_spent) %>% 
  head(5)
```


# What are the top 10 items that are removed from cart?
```{r}
df %>% 
  filter(event_type == 'remove_from_cart') %>% 
  group_by(product_id) %>% 
  count(sort = TRUE) %>% 
  head(10)
```


# Which products have the best purchase to view ratio?
```{r}
df %>% 
  filter(event_type == 'view' | event_type == 'purchase') %>% 
  group_by(product_id, event_type) %>% 
  count() %>% 
  pivot_wider(names_from = event_type, values_from = n) %>% 
  select(product_id, purchase, view) %>% 
  mutate(purchase = replace_na(purchase, 0)) %>% 
  mutate(pv_ratio = purchase/view) %>% 
  arrange(-pv_ratio)
```


# What day of the month do people make the most purchases? and what time of the day?
```{r}
df$event_time <- df$event_time %>% lubridate::ymd_hms(tz = 'UTC')

parsed_event_time <- df %>% 
    mutate(year = lubridate::year(event_time),
           month = lubridate::month(event_time), 
           day = lubridate::day(event_time), 
           time_12 = format(event_time, '%I:%M %p'), 
           time_24 = format(event_time, '%H:%M'), 
           hour_24 = format(event_time, '%H'),
           tz = lubridate::tz(event_time)) %>% 
    mutate(month_day = str_c(month, "/", day)) %>% 
    mutate(year_month_day = str_c(year, "/", month, "/", day)) %>% 
    mutate_at(.vars = vars(year_month_day), .funs = list(~ as.Date(., "%Y/%m/%d"))) %>% 
    mutate(weekday = weekdays(year_month_day))

parsed_event_time %>% 
  filter(event_type == 'purchase') %>%
  group_by(day) %>% 
  count() %>% 
  ggplot(aes(x=day, y=n, group = 1)) + 
    geom_line() + 
    geom_point() +
    ggtitle("purchases by day") + 
    theme(plot.title = element_text(hjust = 0.5))

parsed_event_time %>% 
  filter(event_type == 'purchase') %>%
  group_by(hour_24) %>% 
  count() %>% 
  ggplot(aes(x=hour_24, y=n, group = 1)) + 
    geom_line() + 
    geom_point() +
    ggtitle("purchases by hour") + 
    theme(plot.title = element_text(hjust = 0.5))
```


# What day of the week has the most purchases?  
```{r}
weekday_high <- parsed_event_time %>% 
                    filter(event_type == 'purchase') %>% 
                    group_by(weekday) %>% 
                    count(sort = TRUE) %>% 
                    head(1) %>%
                    pull(n)
days_of_the_week <- c('Monday', 
                      'Tuesday', 
                      'Wednesday', 
                      'Thursday', 
                      'Friday', 
                      'Saturday', 
                      'Sunday')

parsed_event_time %>% 
  filter(event_type == 'purchase') %>% 
  group_by(weekday) %>% 
  count() %>%
  arrange(factor(weekday, levels = days_of_the_week)) %>% 
  ungroup(weekday) %>%
  mutate(weekday = fct_relevel(weekday, days_of_the_week)) %>%
  ggplot(aes(x=weekday, y=n, group=1)) +
    geom_line() + 
    geom_point() + 
    ggtitle("purchases by weekday") + 
    theme(plot.title = element_text(hjust = 0.5)) +
    ylim(0, weekday_high+20000)
```


# Let's track a user's history
```{r}
track_user <- parsed_event_time %>% filter(user_id == 520220043)

track_user %>% 
  filter(event_type == 'purchase') %>% 
  group_by(month_day) %>% 
  count() %>% 
  ggplot(aes(x=month_day, y=n, group=1)) + 
    geom_line() + 
    geom_point() + 
    ggtitle("purchase history of a user") + 
    theme(plot.title = element_text(hjust = 0.5))
```



