---
title: "E-commerce Cosmetics"
author: "Nathan"
date: "12/17/2019"
output: html_document
---

# Exploratory data analysis of an e-commerce cosmetics shop from October 2019 to November 2019.
# source: https://www.kaggle.com/mkechinov/ecommerce-events-history-in-cosmetics-shop


# First, let's load our packages and disable scientific notation.
```{r results = 'hide', message=FALSE, warning=FALSE}
library(tidyverse)
options(scipen = 999)
```


# Now, let's load in the two csv files and combine them into one data.frame.
```{r}
oct2019 <- read.csv("C:/workspaceR/eCommerce_cosmetics/oct2019.csv", stringsAsFactors=FALSE)
nov2019 <- read.csv("C:/workspaceR/eCommerce_cosmetics/nov2019.csv", stringsAsFactors=FALSE)
df <- bind_rows(oct2019, nov2019)

```


# Examine data.
```{r}
df %>% head()
df %>% str()
```


# What are the most purchased brands?
```{r}
df %>% 
  filter(event_type == 'purchase') %>% 
  group_by(brand) %>% 
  count(sort = TRUE) %>% 
  filter(!brand == "")
```

# Who purchased the most products and what do they buy?
```{r}
top_buyer<- df %>% 
              filter(event_type == 'purchase') %>% 
              group_by(user_id) %>% 
              count(sort = TRUE) %>% 
              head(1) %>% 
              pull(user_id)
top_buyer

df %>% 
  filter(event_type == 'purchase' & user_id == top_buyer) %>% 
  group_by(product_id) %>% 
  count(sort = TRUE)
```

# Who are the top 5 buyers in terms of dollar amount? 
```{r}
df %>% 
  filter(event_type == 'purchase') %>% 
  group_by(user_id) %>% 
  summarize(dollars_spent = sum(price)) %>% 
  arrange(-dollars_spent) %>% 
  head(5)
```


# What are the top 10 items that are removed from cart?
```{r}
df %>% 
  filter(event_type == 'remove_from_cart') %>% 
  group_by(product_id) %>% 
  count(sort = TRUE) %>% 
  head(10)
```

# Which products have the best purchase to view ratio?
```{r}
df %>% 
  filter(event_type == 'view' | event_type == 'purchase') %>% 
  group_by(product_id, event_type) %>% 
  count() %>% 
  pivot_wider(names_from = event_type, values_from = n) %>% 
  select(product_id, purchase, view) %>% 
  mutate(purchase = replace_na(purchase, 0)) %>% 
  mutate(pv_ratio = purchase/view) %>% 
  arrange(-pv_ratio)
```



